**The statistical analysis of non-linear longitudinal data in biomedical research**

### 2021-01-05 Manuscripts/Manuscript_AM_v1.Rmd
Does not work on laptop

---
title: '**The statistical analysis of non-linear longitudinal data in biomedical research**'
author:
- Ariel Mundo^[Department of Biomedical Engineering, University of Arkansas, Fayetteville]
- Timothy J. Muldoon^[Department of Biomedical Engineering, University of Arkansas,
  Fayetteville]
- John R. Tipton^[Department of Mathematical Sciences, University of Arkansas, Fayetteville]
subtitle: _Beyond repeated measures ANOVA and Linear Mixed Models_
bibliography: refs.bib
csl: ieee.csl
css: style.css
fontfamily: Arial
  output:

  bookdown::html_document2: default
  bookdown::pdf_document2:
    keep_tex: yes
    fig_caption: yes
  bookdown::word_document2: default
  link-citations: true
---

>>>>

---
title: '**The statistical analysis of non-linear longitudinal data in biomedical research**'
author:
- Ariel Mundo^[Department of Biomedical Engineering, University of Arkansas, Fayetteville]
- Timothy J. Muldoon^[Department of Biomedical Engineering, University of Arkansas,
  Fayetteville]
- John R. Tipton^[Department of Mathematical Sciences, University of Arkansas, Fayetteville]
subtitle: _Beyond repeated measures ANOVA and Linear Mixed Models_
bibliography: refs.bib
csl: ieee.csl
css: style.css
fontfamily: Arial
  output:
  bookdown::html_document2: default
  bookdown::pdf_document2:
    keep_tex: yes
    fig_caption: yes
  bookdown::word_document2: default
  link-citations: true
---
